rbeast2: BEAUti 2, BEAST2 and Tracer for R

### 2018-02-19 article.tex
Indeed do not need TreeSim, thanks @rsetienne
Fix refs
EOD

However, BEAUti cannot be called from a command-line script.
This implies that when the user 
wants to explore the consequences of various settings, this must be done manually.
This is the common workflow when using a few alignments and doing a superficial 
analysis of sensitivity of the reconstructed tree to model settings.

For exploring many trees (for instance from simulations) and for
more thorough sensitivity analysis, one would like to loop through 
multiple (simulated) alignments, nucleotide substitution models, 
clock models and tree priors.

@@

However, for exploring the output of many BEAST2 runs, 
one would like a script to collect all parameters' ESSes,
parameter traces and posterior phylogenies.

@@

\verb;rbeast2; is the first R package that unifies the
full workflow of working with BEAST2. An
example to create a BEAST2 input file is 
\verb;BEASTmasteR; \cite{beastmaster}.
Also \verb;BEASTmasteR; allows 
to create BEAST2 configuration files from R. 
The difference is that \verb;rbeast2; 
has its focus on DNA alignments and ultrametric trees (that
is, trees that have their tips measured in the present), 
where \verb;BEASTmasteR; is used for 
morphological traits and tip-dating.
Examples of R packages to parse the BEAST2 output files
are \verb;rBEAST; \cite{rBEAST} and 
\verb;RBEAST; \cite{RBEAST}.

@@

\verb;rbeast2; uses the Travis CI \cite{travis} 
continuous integration service, which is known to significantly 
increase the the number of bugs exposed \cite{vasilescu2015} and increases
the speed at which new features are added \cite{vasilescu2015}.
\verb;rbeast2; has a 100\% code coverage, which correlates with code quality \cite{horgan1994,del1995correlation}. 
\verb;rbeast2; follows Hadley Wickham's style guide \cite{style_guide}, 
which improves software quality \cite{fang2001}.
\verb;rbeast2; dependends on multiple packages, which are 
\verb;APE; \cite{APE}, 
\verb;beautier; \cite{beautier},
\verb;beastier; \cite{beastier},
\verb;devtools; \cite{devtools},
\verb;geiger; \cite{GEIGER},
\verb;ggplot2; \cite{ggplot2},
\verb;knitr; \cite{knitr},
\verb;phangorn; \cite{phangorn},
\verb;rmarkdown; \cite{rmarkdown},
\verb;seqinr; \cite{seqinr},
\verb;stringr; \cite{stringr},
\verb;testit; \cite{testit} and 
\verb;tracerer; \cite{tracerer} and
\verb;TreeSim; \cite{TreeSim}.

>>>>

However, BEAUti cannot be called from a command-line script.
This implies that when the user 
wants to explore the consequences of various settings, this must be done manually.
This is the common workflow when using a few alignments and doing a superficial 
analysis of sensitivity of the reconstructed tree to model settings. 
For exploring many trees (for instance from simulations) and for
more thorough sensitivity analysis, one would like to loop through 
multiple (simulated) alignments, nucleotide substitution models, 
clock models and tree priors. 
One such tool to replace 
BEAUti is \verb;BEASTmasteR; \cite{beastmaster},
which focuses on morphological traits and tip-dating, but also 
supports DNA data.

@@

However, for exploring the output of many BEAST2 runs, 
one would like a script to collect all parameters' ESSes,
parameter traces and posterior phylogenies. 
Examples of R packages to do some of these
are \verb;rBEAST; \cite{rBEAST_ratmann} and 
\verb;RBeast; \cite{RBeast_faria}.

@@

\verb;rbeast2; is the first R package that unifies the
full workflow of working with BEAST2. 
Where \verb;BEASTmasteR; needs dozens for lines to create
a BEAST2 configuration file, with \verb;rbeast2; the same 
can be created by a simple one-liner. Unlike \verb;rBEAST; 
and \verb;RBeast;, \verb;rbeast2; implements all of Tracer's
primary functionality. This makes \verb;rbeast2; a complete 
solution for using BEAST2 from R.

@@

\verb;rbeast2; uses the Travis CI \cite{travis} 
continuous integration service, which is known to significantly 
increase the the number of bugs exposed \cite{vasilescu2015} and increases
the speed at which new features are added \cite{vasilescu2015}.
\verb;rbeast2; has a 100\% code coverage, which correlates with code quality \cite{horgan1994,del1995correlation}. 
\verb;rbeast2; follows Hadley Wickham's style guide \cite{style_guide}, 
which improves software quality \cite{fang2001}.
\verb;rbeast2; dependends on multiple packages, which are 
\verb;APE; \cite{APE}, 
\verb;beautier; \cite{beautier},
\verb;beastier; \cite{beastier},
\verb;devtools; \cite{devtools},
\verb;geiger; \cite{GEIGER},
\verb;ggplot2; \cite{ggplot2},
\verb;knitr; \cite{knitr},
\verb;phangorn; \cite{phangorn},
\verb;rmarkdown; \cite{rmarkdown},
\verb;seqinr; \cite{seqinr},
\verb;stringr; \cite{stringr},
\verb;testit; \cite{testit} and 
\verb;tracerer; \cite{tracerer}.
